RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-08-21 manuscripts/manuscript.Rmd
added comment about phylobase reference

There are many promising directions for further development of the
`RNeXML` package.  The project's [Milestones page](https://github.com/ropensci/RNeXML/issues/milestones) page provides a list of
steps currently planned or under consideration.  In particular, these
milestones include increased support for interactive mode of entering data
(wizards), conversions to and from other existing R phylogenetics formats
such those found in the `phylobase` package [@phylobase],
and support for integration of semantics defined through the
Web Ontology language (OWL), as discussed in the Challenges section.

>>>>

There are many promising directions for further development of the
`RNeXML` package.  The project's [Milestones page](https://github.com/ropensci/RNeXML/issues/milestones) page provides a list of
steps currently planned or under consideration.  In particular, these
milestones include increased support for interactive mode of entering data
(wizards), conversions to and from other existing R phylogenetics formats
such those found in the `phylobase` package [@phylobase],
<!-- hmm, phylobase ref renders for me as 'al. 2014' -->
and support for integration of semantics defined through the
Web Ontology language (OWL), as discussed in the Challenges section.
